---
title: "Final Presentation"
author: "Author: Laurel Brawley"
date: "`r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: ioslides_presentation
---
```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## Packages Used


## World Happiness Report 2022

I got my data set from https://www.kaggle.com/code/prakhosha/world-happiness-analysis

This data was last updated on April 20th, 2022.

**Variables in the Dataset:**

*Happiest_Countries: top 10 happiest countries in the world

*Saddest_Countries: last 10 countries ranked in happiness in the world

*Full: general rankings of the countries

*Score: the score of the country




##
```{r}
Happiest_Countries <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
Score <- c(7.821, 7.636, 7.557, 7.512, 7.415, 7.404, 7.384, 7.365, 7.364, 7.2)

plot(Happiest_Countries, Score)
```

Top 10 Happiest Countries: Finland, Denmark, Iceland, Swizterland, Netherlands, Luxemburg, Sweden, Norway, Israel, and New Zealand

##
```{r}
Unhappiest_Countries <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
Score2 <- c(2.404, 2.955, 2.995, 3.268, 3.471, 3.512, 3.574, 3.702, 3.750, 3.760)

plot(Unhappiest_Countries, Score2)
```

Top 10 Saddest Countries: Afghanistan, Lebanon, Zimbabwe, Rwanda, Botswana, Lesotho, Sierra Leone, Tanzania, Malawi, Zambia.

##
```{r}
Full <- c(1, 25, 50, 75, 100, 125, 146)
Score3 <- c(7.821, 6.523, 6.106, 5.547, 5.06, 4.396, 2.404)

plot(Score3, Full, type = "l")
```

This final graph shows the full scale of happiness as it goes through all the countries of the world.
The United States is 16th, with a score of 6.977